---
title: "Assignment6"
author: "Sharik Baig"
date: "06/11/2022"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
getwd()
setwd("C:/Users/shari/OneDrive/Desktop/Business Analytics/QMM/Assignment6")
```

## Question 2 - Research and Development Division of Emax Corporation

Based on the problem statement, the goal is to:

Maximize Z = P - 6*C - 3*D

  P = total (discounted) profit over the life of the new products,
  C = change (in either direction) in the current level of employment,
  D = decrease (if any) in next year’s earnings from the current year’s level.

Subject to:

Total Profit: Maximize P = 20*X1 + 15*X2 + 25*X3

Employment Level: 6*X1 + 4*X2 + 5*X3 = 50

Earnings Next Year: 8*X1 + 7*X2 + 5*X3 >= 75

As a result, the auxillery variables become:

Y1 = 6*X1 + 4*X2 + 5*X3 - 50
Y2 = 8*X1 + 7*X2 + 5*X3 - 75

Which becomes:

(Y1P - Y1M) = 6*X1 + 4*X2 + 5*X3 - 50
(Y2P - Y2M) = 8*X1 + 7*X2 + 5*X3 - 75

Therefore, the final setup of the problem statement is:

Maximize Z = 20*X1 + 15*X2 + 25*X3 - 6*Y1P - 6*Y1M - 3*Y2M

Subject to:

6*X1 + 4*X2 + 5*X3 - (Y1P - Y1M) = 50
8*X1 + 7*X2 + 5*X3 - (Y2P - Y2M) = 75

And:

X1, X2, X3 >= 0
Y1P, Y1M, Y2P, Y2M >= 0

Lastly, we will run this problem in R as a linear programming model and discuss the results.

```{r}
# This problem will require the "lpSolveAPI" library
require(lpSolveAPI)
```


```{r}
# Import the .lp file for this problem
lpm <- read.lp(filename="emax.lp",type = "lp")
# Return the linear programming model
lpm
```

```{r}
# Solve the linear programming model
solve(lpm)
get.objective(lpm)
get.variables(lpm)
```

Based on the output of the linear programming model, we can conclude several things.

X1 = 0
X2 = 0
X3 = 15
Y1P = 25
Y1M = 0
Y2M = 0
Y2P = 0

Therefore, we can conclude that the product mix should only contain product 3. With this mix, there would be an object value of 225 units. The goal for earnings next year is fully met; however, the employment level goal will be exceeded by 25 units, which correlates to 2,500 employees and a penalty of 150 units to the objective function.