---
title: "Sbaig1_Assignment3"
author: "Sharik Baig"
date: "18/10/2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Problem Statement:

Heart Start produces automated external defibrillators (AEDs) in each of two different plants (A and B). The unit production costs and monthly production capacity of the two plants are indicated in the table below. The AEDs are sold through three wholesalers. The shipping cost from each plant to the warehouse of each wholesaler along with the monthly demand from each wholesaler are also indicated in the table. How many AEDs should be produced in each plant, and how should they be distributed to each of the three wholesaler warehouses so as to minimize the combined cost of production and shipping? 

• Formulate a transportation problem. 
• Solve a transportation problem 
• Formulate the dual of the transportation problem 
• Interpret the dual of transportation problem

```{r}
HeartStart <- matrix(c(22,14,30,600,100 ,
16,20,24,625,120,
80,60,70,"-","-" ), ncol=5, byrow=TRUE)
colnames(HeartStart) <- c("Warehouse 1", "Warehouse 2", "Warehouse 3","Production cost","Production Capacity")
rownames(HeartStart) <- c("Plant A", "Plant B","Monthly Demand")
HeartStart <- as.table(HeartStart)
HeartStart
```
Formulating the LP below:

$$ \text{Min} \hspace{.2cm} TC = 22 x_{11} +14 x_{12} +30 x_{13}$$
$$\hspace{2cm}+16 x_{21}+20 x_{22}+ 24 x_{23}$$
$$\hspace{2cm}+80 x_{31}+ 60 x_{32}+ 70 x_{33}$$
Supply constraints

$$x_{11} + x_{12} + x_{13}\le 100$$
$$x_{21} + x_{22} + x_{23}\le 120$$
Demand Constraints

$$x_{11} +x_{21}\ge 80$$
$$x_{12} +x_{22}\ge 60$$
$$x_{13} +x_{23}\ge 70$$
Non-Negativity of the variables

$$x_{ij}\ge 0$$ \text{where}$$ i= 1,2,3$$ \text{and}$$j= 1,2,3$$
```{r}
library(lpSolve)

#Cost matrix

costs <- matrix(c(622,614,630,0,
641,645,649,0), ncol = 4,byrow = TRUE)

#Plant names

colnames(costs) <- c("Warehouse 1", "Warehouse 2","Warehouse 3","Dummy")
rownames(costs) <- c("Plant A", "Plant B")
costs
```

#Supply side constraints

```{r}
row.signs <- rep("<=", 2)
row.rhs <- c(100,120)
```

#Demand (sinks) side constraints

```{r}
col.signs <- rep(">=", 4)
col.rhs <- c(80,60,70,10)
```

#Execute

```{r}
lptrans <- lp.transport(costs, "min", row.signs, row.rhs, col.signs, col.rhs)
```

#Variable values

```{r}
lptrans$solution
```

# objective function value

```{r}
lptrans$objval
```

#Constraints value

```{r}
lptrans$solution
```
Summary of the optimal solution to minimize the cost of production and shipping.

1. Plant 2: Ware House 1 should produce 80 AEDs
2. Plant 1: Ware House 2 should produce 60 AEDs
3. Plant 1: Ware House 3 should produce 40 AEDs
4. Plant 2: Ware House 3 should produce 30 AEDs
5. Plant 2: Ware House 4 should produce 10 AEDs

#Formulating the dual of above problem.

$$ \text{Maximize VA} \hspace{.2cm}= 100 P_{1} +120 P_{2} -80W_{1}- 60W_{2}- 70W_{3}$$
Subject to the following constraints


$$ \ Total \hspace{.2cm} Profit \hspace{.2cm} Constraints$$

$$MR_{1} - MC_{1} \ge = 622$$
$$MR_{2} - MC_{1} \ge = 614$$
$$MR_{3} - MC_{1} \ge = 630$$
$$MR_{1} - MC_{2} \ge = 641$$
$$MR_{2} - MC_{2} \ge = 645$$
$$MR_{3} - MC{2} \ge = 649$$
$$Where\hspace{.2cm} MR_{1} = Marginal\hspace{.2cm} Revenue\hspace{.2cm}from\hspace{.2cm} Warehouse 1$$
$$MR_{2} = Marginal\hspace{.2cm}Revenue\hspace{.2cm} from\hspace{.2cm}Warehouse 2$$
$$MR_{3} = Marginal\hspace{.2cm} Revenue\hspace{.2cm} from\hspace{.2cm}Warehouse 3$$
$$MC_{1} = Marginal\hspace{.2cm} Cost\hspace{.2cm} from\hspace{.2cm}Plant 1$$
$$MC_{2} = Marginal\hspace{.2cm} Cost\hspace{.2cm} from\hspace{.2cm}Plant 2$$




$$Economic\hspace{.2cm} Interpretation\hspace{.2cm} of\hspace{.2cm} the\hspace{.2cm} dual$$
$$MR_{1} >= MC_{1} + 622$$
$$MR_{2} >= MC_{1} + 614$$
$$MR_{3} >= MC_{1} + 630$$
$$MR_{1} >= MC_{2} + 641$$
$$MR_{2} >= MC_{2} + 645$$
$$MR_{3} >= MC_{2} + 649$$
The above constraints framed under the economic interpretation of the dual follows the universal rule of profit maximization i.e. MR >= MC where “MR” is the Marginal Revenue and “MC” is the Marginal Cost.
$$MR_{1} >= MC_{1} + 621\hspace{.4cm}i.e.\hspace{.4cm} MR_{1} >= MC_{1}$$
Marginal Revenue i.e. The revenue generated for each additional unit sold relative to Marginal Cost (MC) i.e. The change in cost at Plant 1 by inducing an increase in the supply function should be greater than or equal to the revenue generated for each additional unit distributed to Warehouse 1.

