---
title: "Sbaig1_Assignment2"
author: "Sharik Baig"
date: "13/09/2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(lpSolveAPI)
```

```{r}
setwd("C:/Users/shari/OneDrive/Desktop/Business Analytics/QMM/Assignment2")

##a linear program with 9 decision variables and 0 constraints

lp <- make.lp(0,9, verbose = "neutral")
lp
```


```{r}
## Model name: 
##   a linear program with 9 decision variables and 0 constraints
## Add the constraints
add.constraint(lp, c(1,1,1,0,0,0,0,0,0), "<=", 750 )
add.constraint(lp, c(0,0,0,1,1,1,0,0,0), "<=", 900)
add.constraint(lp, c(0,0,0,0,0,0,1,1,1), "<=", 450)
add.constraint(lp, c(20,15,12,0,0,0,0,0,0), "<=", 13000)
add.constraint(lp, c(0,0,0,20,15,12,0,0,0), "<=", 12000)
add.constraint(lp, c(0,0,0,0,0,0,20,15,12), "<=", 5000)
add.constraint(lp, c(1,1,1,0,0,0,0,0,0), "<=", 900)
add.constraint(lp, c(0,0,0,1,1,1,0,0,0), "<=", 1200)
add.constraint(lp, c(0,0,0,0,0,0,1,1,1), "<=", 750)
add.constraint(lp, c(6, 6, 6, -5, -5, -5, 0, 0, 0), "=", 0)
add.constraint(lp, c( 3, 3, 3, 0, 0, 0, -5, -5, -5), "=", 0)
```

```{r}
## Create objective function. We need maximum profit so change sense to max
set.objfn(lp, c(420,360,300,420,360,300,420,360,300))
lp.control(lp, sense='max')
```

## $anti.degen
## [1] "none"
## 
## $basis.crash
## [1] "none"
## 
## $bb.depthlimit
## [1] -50
## 
## $bb.floorfirst
## [1] "automatic"
## 
## $bb.rule
## [1] "pseudononint" "greedy"       "dynamic"      "rcostfixing" 
## 
## $break.at.first
## [1] FALSE
## 
## $break.at.value
## [1] 1e+30
## 
## $epsilon
##       epsb       epsd      epsel     epsint epsperturb   epspivot 
##      1e-10      1e-09      1e-12      1e-07      1e-05      2e-07 
## 
## $improve
## [1] "dualfeas" "thetagap"
## 
## $infinite
## [1] 1e+30
## 
## $maxpivot
## [1] 250
## 
## $mip.gap
## absolute relative 
##    1e-11    1e-11 
## 
## $negrange
## [1] -1e+06
## 
## $obj.in.basis
## [1] TRUE
## 
## $pivoting
## [1] "devex"    "adaptive"
## 
## $presolve
## [1] "none"
## 
## $scalelimit
## [1] 5
## 
## $scaling
## [1] "geometric"   "equilibrate" "integers"   
## 
## $sense
## [1] "maximize"
## 
## $simplextype
## [1] "dual"   "primal"
## 
## $timeout
## [1] 0
## 
## $verbose
## [1] "neutral"
## To identify the variables and constraints, Set the variable names and the constraints ## set.bounds(lp, lower = c(0, 0, 0, 0, 0, 0, 0, 0, 0), columns = c(1,2,3,4,5,6,7,8,9))

```{r}
RowNames <- c("Con1", "Con2", "Con3", "storage1", "Storage2", "Storage33", "Sale1", "Sale2", "Sale3", "%C1", "%C2")
ColNames <- c("Large1", "Medium1", "Small1", "Large2", "Medium2", "Small2", "Large3", "Medium3", "Small3")
dimnames(lp) <- list(RowNames, ColNames)
lp
```

```{r}
## Model name: 
##   a linear program with 9 decision variables and 11 constraints
write.lp(lp, filename = "QMMAssignment2.lp", type = "lp")
solve(lp)
## [1] 0
get.objective(lp)
## [1] 696000
get.variables(lp)
## [1] 516.6667 177.7778   0.0000   0.0000 666.6667 166.6667   0.0000   0.0000
## [9] 416.6667
```
